---
title: "Transitivy and clustering"
output: html_document
author: Anya Bataeva
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
#uploading data
library(igraph)
library(ggraph)
library(readr)
library(dplyr)
library(ggplot2)
options(scipen = 999)


m = read.csv(url("https://raw.githubusercontent.com/fyzbt/SNAseminars/master/data/LONDON_GANG.csv"), header=T, row.names=1) # загружаем датасет со связями
m = ifelse(m != 1, 0, 1)
m = as.matrix(m)

gang = graph.adjacency(m, mode="undirected", weighted=NULL, diag=FALSE)
plot(gang, vertex.label=NA)
```

# Transitivity

types of transitivity in R

list("global")
The global transitivity of an undirected graph (directed graphs are considered as undirected ones as well). This is simply the ratio of the triangles and the connected triples in the graph. For directed graph the direction of the edges is ignored.

list("local")
The local transitivity of an undirected graph, this is calculated for each vertex given in the vids argument. The local transitivity of a vertex is the ratio of the triangles connected to the vertex and the triples centered on the vertex. For directed graph the direction of the edges is ignored.

list("undirected")
This is the same as global.

list("globalundirected")
This is the same as global.

list("localundirected")
This is the same as local.

list("barrat")
The weighted transitivity as defined A. Barrat. See details below.

list("weighted")
The same as barrat.


```{r echo=FALSE, warning=FALSE}
transitivity(gang, type="global")
```

```{r echo=FALSE, warning=FALSE}
local_transit = transitivity(gang, type="local")
V(gang)$transit = local_transit
ggraph(gang, layout = "fr") +
  geom_edge_link(width=0.3, show.legend = FALSE) +
  geom_node_point(aes(size=transit*10), alpha = 0.7) +
  theme_void() +
  theme(legend.position="none", text=element_text(family="Times New Roman"))
```

```{r echo=FALSE, warning=FALSE}
transitivity(gang, type="undirected")
```

```{r echo=FALSE, warning=FALSE}
transitivity(gang, type="barrat")
```


# Clustering coefficient
```{r}
library(NetworkToolbox)
cl_coeff <- clustcoeff(m, weighted = FALSE)
```
Global clustering coefficient
```{r}
cl_coeff$CC
```
Local clustering coefficient
```{r}
cl_coeff$CCi
cl_coeff_CCi <- as.data.frame(cl_coeff$CCi) %>% mutate(name=rownames(cl_coeff_CCi)) 
colnames(cl_coeff_CCi)[1] <- "coeff"
cl_coeff_CCi <- cl_coeff_CCi %>% select(name, coeff)
```

# Community detection algos

```{r}
library(stringr)
m<-read.csv(file.choose(),header=T,row.names=1)

m1<-ifelse (m != 1, 0, 1)

m1<-as.matrix(m1)
gang <- graph.adjacency(m1,mode="undirected",
                            weighted=NULL, diag=FALSE)
gang = delete.vertices(gang, V(gang)[degree(gang) < 1])

la<-layout_nicely(gang)
plot(gang, layout=la, vertex.size=3,edge.width=e.wt,
     vertex.label=NA)

```

Коммьюнити детекшн

```{r}
#КЛИКИИИ

cliques(gang,min=3) # list of cliques
sapply(cliques(gang,min=3), length)  # размеры клик
largest_cliques(gang) # самые большие клики


#КОРЫЫЫ
kcore <- coreness(gang)    
V(gang)$core <- kcore   
plot.igraph(gang, vertex.color=V(gang)$core, vertex.label=NA)#один из вариантов визуализации


#ЛУВЭЙН
lvc <- cluster_louvain(gang)
lvc
sizes(lvc)
V(gang)$lvc<-cluster_louvain(gang)


```

Картиночки

```{r}
#cliques
set.seed(42)
vcol <- rep("grey80", vcount(gang))
vcol[unlist(largest_cliques(gang))] <- "gold"
plot(as.undirected(gang), vertex.label=NA, vertex.color=vcol,vertex.size=6,edge.width=0.7)



#k-cores
set.seed(42)
colrs <- adjustcolor( c("gray50", "tomato", "gold", "yellowgreen","lightblue","darkslateblue"), alpha=.6)
 kc <- coreness(gang)
plot(gang, vertex.size=kc*3, vertex.label=kc, vertex.color=colrs[kc])
coreness(gang)


#Louvaine
set.seed(42)
plot(lvc, gang,
     edge.widh=0.3,
     vertex.label = NA, vertex.size=6,
     layout = layout_with_kk)

```

# Articulation points
```{r}
articulation.points(gang)

V(gang)$color <- "grey80"

##  Set articulation points to red:
V(gang)$color[ articulation.points(gang) ] <- "gold"
V(gang)$betweenness = igraph::betweenness(gang)

##  Set bridge edges to red:
num_comp <- length( decompose.graph(gang) )
for (i in 1:length(E(gang))) {
  G_sub <- delete.edges(gang, i)
  if ( length( decompose.graph(G_sub) ) > num_comp ) E(gang)$color[i] <- "red"
}

set.seed(42)
V(gang)$label.cex <- 0.7
V(gang)$Prison = LONDON_GANG_ATTR$Prison
V(gang)$color=V(gang)$Prison
V(gang)$color=gsub("1","gold", V(gang)$color) #Females will be red
V(gang)$color=gsub("0","grey80", V(gang)$color)
col = V(gang)$color

set.seed(42)
plot(gang, layout = layout.fruchterman.reingold, 
     vertex.size = 6,
     vertex.color= col,
     vertex.label = ifelse(V(gang) %in% articulation.points(gang), V(gang), NA),
     vertex.label.dist = 0,
     vertex.label.font = 2,
     edge.color=E(gang)$color,
     edge.width=0.7)

#би компоненты
bc <- biconnected_components(gang)
summary(bc)

largest_component <- lapply(biconnected_components(gang)$components, 
                            length) %>% which.max()

V(gang)$color <- 
  ifelse(V(gang) %in%
           biconnected_components(gang)$components[[largest_component]],
         "grey80","gold")
E(gang)$color <- "black"
set.seed(42)
plot(gang, layout = layout.fruchterman.reingold, 
     #vertex.label = V(G)$name,
     vertex.label = NA,
     vertex.size = 6)
```

таблица с саммари по всем метрикам (дигри, клозенес, битвиность, eigen vector centrality)
```{r}
ptable = as.data.frame(cbind(degree(gang), closeness(gang), betweenness(gang), round(evcent(gang)$vector, 3)))
```
