---
title: "Бимодальные сети и юнимодельная проекция"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
```

```{r}
#загрузка данных
library(readr)
library(dplyr)
library(igraph)
library(ggraph)


davis123 = read.csv(url("https://docs.google.com/spreadsheets/d/e/2PACX-1vTiAMX0tLhgRGfSSIZap66_80I-UVDYmGQ8EOZHTieIRv4TX7e8dJVPq8O52sDbn2O9mVmRbURVpsoM/pub?output=csv"))

g <- graph.data.frame(davis123, directed=FALSE)
```

```{r}
bipartite.mapping(g)
```

```{r}

V(g)$type <- bipartite_mapping(g)$type  ## Add the "type" attribute
                                            ##  to the network.
```
###Построение сетей (бимодальные данные) 
####Первоначальные данные
#####Визуализация
```{r include=FALSE}
plot(g)
```

```{r include=FALSE}
plot(g, vertex.label.cex = 0.8, vertex.label.color = "black")
```

```{r}
V(g)$color <- ifelse(V(g)$type, "#b0aac0", "#ddeedd")
V(g)$shape <- ifelse(V(g)$type, "circle", "square")
E(g)$color <- "lightgray"
  
plot(g, vertex.label.cex = 0.8, vertex.label.color = "black")
```

####Немного изменяем размер
```{r}
V(g)$label.color <- "black" ##ifelse(V(g)$type, "black", "white")
## V(g)$label.font <-  2
V(g)$label.cex <- 1 ##ifelse(V(g)$type, 0.8, 1.2)
## V(g)$label.dist <-0
V(g)$frame.color <-  "gray"
V(g)$size <- 18

plot(g, layout = layout_with_graphopt)
```

####Строим такцю же сеть, но с иным лейаутом
```{r}
plot(g, layout=layout.bipartite, vertex.size=8, vertex.label.cex=0.6)
```

####Вычисляем меры узловой центральности
```{r}
types <- V(g)$type                 ## getting each vertex `type` let's us sort easily
deg <- degree(g)
betw <- betweenness(g)
clos <- closeness(g)
eig <- eigen_centrality(g)$vector

cent_df <- data.frame(types, deg, betw, clos, eig)

cent_df[order(cent_df$type, decreasing = TRUE),] ## sort w/ `order` by `type`

```
####Добавляем на сеть данные о дегри узла
```{r}
V(g)$size <- degree(g)
V(g)$label.cex <- degree(g) * 0.2

plot(g, layout = layout_with_graphopt)

```

###Converting Two-Mode to One-Mode Networks

```{r}
bipartite_matrix <- as_incidence_matrix(g)
bipartite_matrix
```
```{r}
t(bipartite_matrix)
```

###Matrix Multiplication - For Overlap Count
```{r}
event_matrix_prod <- t(bipartite_matrix) %*% bipartite_matrix 

## crossprod() does same and scales better, but this is better to learn at first at first so you understand the method

diag(event_matrix_prod) <- 0

event_matrix_prod


```

```{r}
person_matrix_prod <- bipartite_matrix %*% t(bipartite_matrix)

diag(person_matrix_prod) <- 0

person_matrix_prod
```

####women_overlap
```{r}

women_overlap <- graph_from_adjacency_matrix(person_matrix_prod, 
                                        mode = "undirected", 
                                        weighted = TRUE)
women_overlap

V(women_overlap)$color <- "#b0aac0"

plot(women_overlap)
```

####events_overlap
```{r}
events_overlap <- graph_from_adjacency_matrix(event_matrix_prod, 
                                       mode = "undirected", 
                                       weighted = TRUE)

events_overlap

V(events_overlap)$color <- "#ddeedd"

plot(events_overlap)
```

###Bipartite_projection
```{r}
projected_g <- bipartite_projection(g, multiplicity = TRUE)


```
```{r}
events_auto_projected <- projected_g$proj1
south_women_auto_projected <- projected_g$proj2

events_auto_projected
south_women_auto_projected
```

####Bipartite_projection Women
```{r}
plot(events_auto_projected)
```

####Bipartite_projection Event
```{r}
plot(south_women_auto_projected)
```


###Jaccard Similarity
####Jaccard woman

```{r}
library(ade4) # If you have not already done so

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_jaccard <- dist.binary(bipartite_matrix, method=1, upper=TRUE, diag = FALSE) # Method #1 is "Jaccard Index"
event_jaccard <- dist.binary(t(bipartite_matrix), method=1, upper=TRUE, diag = FALSE) 

women_jaccard <- as.matrix(women_jaccard)   
diag(women_jaccard)<-0

# women_jaccard          # Look at the matrix before you binarize
jaccard_women <- ifelse(women_jaccard>0.95, 1, 0)     # Binarize

# jaccard_women      # Take a look at the matrix if you like.

jacc_women <- graph_from_adjacency_matrix(jaccard_women,    # Create an igraph network
                                        mode = "undirected")
V(jacc_women)$color <- "#b0aac0"
plot(jacc_women)
```

####Jaccard event
```{r}
library(ade4) # If you have not already done so

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_jaccard <- dist.binary(bipartite_matrix, method=1, upper=TRUE, diag = FALSE) # Method #1 is "Jaccard Index"
event_jaccard <- dist.binary(t(bipartite_matrix), method=1, upper=TRUE, diag = FALSE) 

event_jaccard <- as.matrix(event_jaccard)   
diag(event_jaccard)<-0

# women_jaccard          # Look at the matrix before you binarize
jaccard_event <- ifelse(event_jaccard>0.95, 1, 0)     # Binarize

# jaccard_women      # Take a look at the matrix if you like.

jacc_event <- graph_from_adjacency_matrix(jaccard_event,    # Create an igraph network
                                        mode = "undirected")
V(jacc_event)$color <- "#ddeedd"
plot(jacc_event)
```


###Pearson’s Correlation
####Women corellation
```{r}

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_correl <- cor(t(bipartite_matrix))
event_correl <- cor(bipartite_matrix)

women_correl <- as.matrix(women_correl)   
# women_correl          # Look at the matrix before you binarize
correl_women <- ifelse(women_correl>0.6, 1, 0)    # Binarize 
diag(correl_women)<-0
# correl_women    # Take a look at the matrix if you like


corr_women <- graph_from_adjacency_matrix(correl_women,     # Create an igraph network
                                        mode = "undirected")

V(corr_women)$color <- "#b0aac0"
plot(corr_women)
```

####Event correlation
```{r}

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_correl <- cor(t(bipartite_matrix))
event_correl <- cor(bipartite_matrix)

event_correl <- as.matrix(event_correl)   
# women_correl          # Look at the matrix before you binarize
event_correl <- ifelse(event_correl>0.6, 1, 0)    # Binarize 
diag(event_correl)<-0
# correl_women    # Take a look at the matrix if you like


event_correl <- graph_from_adjacency_matrix(event_correl,     # Create an igraph network
                                        mode = "undirected")

V(event_correl)$color <- "#ddeedd"
plot(event_correl)
```

###Yule’s Q

####women_Q
```{r}
library(psych)

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_Q <-YuleCor(t(bipartite_matrix))$rho
event_Q <-YuleCor(bipartite_matrix)$rho

women_Q <- as.matrix(women_Q) 
women_Q        # Look at the matrix before you binarize


Q_women <- ifelse(women_Q>0.9, 1, 0) # Binarize
diag(Q_women)<-0
# Q_women    # Take a look at the matrix

YQ_women <- graph_from_adjacency_matrix(Q_women,     # Create an igraph network
                                        mode = "undirected")
V(YQ_women)$color <- "#b0aac0"
plot(YQ_women)

```

####event_Q
```{r}
library(psych)

bipartite_matrix <- as_incidence_matrix(g)  # Extract the matrix

women_Q <-YuleCor(t(bipartite_matrix))$rho
event_Q <-YuleCor(bipartite_matrix)$rho

event_Q <- as.matrix(event_Q) 
event_Q        # Look at the matrix before you binarize


event_Q <- ifelse(event_Q>0.9, 1, 0) # Binarize
diag(event_Q)<-0
# Q_women    # Take a look at the matrix

event_Q <- graph_from_adjacency_matrix(event_Q,     # Create an igraph network
                                        mode = "undirected")
V(event_Q)$color <- "#ddeedd"
plot(event_Q)

```
